Effect of Black Hole Spin on Christodoulou Memory

### 2019-02-14 notes/Paper.tex
updated references

\subsection{CONCLUSIONS}
Observation of Christodoulou memory would be an important test of general relativity in strong field regime. Effort to detect this memory effect in low frequency band from super massive black holes have been undertaken by pulsar timing array experiments. In these experiment the spin effect have been neglected for modeling the signal. It is highly likely that super massive black holes have significant spin due to accretion of matter from surrounding. We have shown in this paper that spin contribution can significantly change the Christodoulou memory. Hence it is important to consider the spin effect while modeling the signals.

>>>>

\subsection{CONCLUSIONS}
Observation of Christodoulou memory would be an important test of general relativity in strong field regime. Effort to detect this memory effect in low frequency band from super massive black holes have been undertaken by pulsar timing array experiments \cite{Pshirkov2010}. In these experiment the spin effect have been neglected for modeling the signal. It is highly likely that super massive black holes have significant spin due to accretion of matter from surrounding. We have shown in this paper that spin contribution can significantly change the Christodoulou memory. Hence it is important to consider the spin effect while modeling the signals.
